\documentclass[12]{article}

% packages
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{enumerate}
\usepackage{setspace}

\title{Project 2 meeting records}
\author{Martin Guyer,  Feifei  Lei \\ Bin Zhuo, Kalbi Zongo}
\date{\today}


\begin{document}

\maketitle

\section{We met on Thursday May 1, 2014 at 2pm. All member were present}

We discussed\\
\begin{enumerate}


\item how to measure the worse delay: we agree to estimate the proportion of flights with departure delays per airport; we also want to add the average delay time per airport.


\item we figured out R code to compute the proportion of flights with departure delays and the average delay time per airport


\item we discuss how to take into account seasonality, and decided to look at the proportion and average delay time per quarter.


\item we wanted to stratify by the airport size (annual number of flights per airport).


\item we split the work: Bin \& Martin are responsible of providing the code to answer our questions, Lei is taking care of the PPT, and kalbi will write the paper.
\end{enumerate}

\section{Monday May 5, 2014 in class. All member were present}
We discussed\\
\begin{enumerate}
\item our population of interest- Charlotte mentioned that we have the possibility to consider data for  the last five years as our population of interest, we did agree to do so.
\item we agreed to exclude airport with annual number of flights less than 10
\item we agreed to sample flights in each airport. Further works include finding sample size (to be taken in our population of interest) and sample size in each airport. We talk about splitting the sample proportionally to the number of flights in each airport. 
Coordinator will figure out next meeting
\end{enumerate}

\section{Next meeting}




\section{Next meeting}


\end{document}
